---
title: "Weight per MPG"
author: "pulin"
date: "12/13/2020"
output:
  slidy_presentation: default
  ioslides_presentation: default
---


## MT CARS
```{r mtcars, echo = TRUE}
summary(mtcars)
```

## Agenda
This dataset has various columns. We are trying to predict weight of a Car in this dataset using 2 models.

## Model1 With Red Line
We will try to predict the Weight of the Car using miles per gallon of a given car and 
try to predict what will be the weight of that car

## Model2 with Blue Line
We will try to predict the Weight of the Car using condition that:
if miles per gallon of a given car is above 20, we will reduce it by 20 MPG.
The model2 uses both MPG and this new set of values as a predictor and 
then try to predict what will be the weight of that car.

## Slider "What is the MPG of the car?"
It will have initial value of 20 MPG. The User can slide left-right to adjust at 
which MPG would they like to predict weight of the car.

## MPG as input
The server will try to compute the weight using Model 1 and 2. It will generate
a Plot with red line showing Model1 and blue line showing Model2. On that line,
it will show point of prediction on each model. Below that,it will also show 
numerical prediction of weight of the car

## Model 1 Summary
```{r }
Model1<-lm(wt ~ mpg, data=mtcars)
summary(Model1)
```

## Model 2 Summary
```{r }
mtcars$mpgsp <- ifelse(mtcars$mpg - 20 > 0, 
                           mtcars$mpg - 20,0)
Model2<-lm(wt ~ mpgsp + mpg, data = mtcars)
summary(Model2)
```

## Other Controls
The user can also show or hide Model1 and Model 2. Initially they will be set to show both.